Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics

### 2019-04-10 tex/MesnardoBarba2019.tex
Add comments about Poisson results

CFD algorithms often require to solve linear systems with iterative methods.
For example, the projection method implemented in our software solve a Poisson system every time step to project the velocity field onto the divergence-free space (to satisfy the incompressibility constraint).
Thus, we investigated the time-to-solution to solve a three-dimensional Poisson system (obtained with a 7-point stencil central-difference scheme) on different nodes of Microsoft Azure and Colonial One.
The system was solved using a Conjugate-Gradient (CG) method with a classical Algebraic Multi-Grid (AMG) preconditioner with an exit criterion set to an absolute tolerance of $10^{-12}$.
The iterative solver ran on CPU nodes (\texttt{H16r} instances on Azure and \texttt{Short} nodes on Colonial One) using the CG algorithm from the PETSc library\cite{balay_et_al_2018} and an AMG preconditioner from Hypre BoomerAMG.
Fig. \ref{fig:poisson_benchmarks} (top) reports the mean runtimes (averaged over $5$ repetitions) to iteratively solve the system, on a uniform grid of $50$ million cells ($1000 \times 1000 \times 50$), as we increase the number of nodes in the pool.
We also solved the Poisson system with the NVIDIA AmgX library on multiple GPU devices using \texttt{NC24r} instances on Azure and \texttt{Ivygpu} nodes on Colonial One.
The Poisson system for a base mesh of $6.25$ million cells ($500 \times 500 \times 25$) is solved on a single node using $12$ MPI processes and $2$ GPU devices; we then double the mesh size as we double the number of nodes.
As the number of iterations to reach convergence increases with the size of the system, we normalize the runtimes by the number of iterations.
Fig. \ref{fig:poisson_benchmarks} (bottom left) shows the normalized mean runtimes ($5$ repetitions) obtained on Azure and Colonial One.
The bottom-right panel of the figure reports the normalized mean runtimes obtained on Azure when we put more constraint on the bandwidth; the base mesh now contains $25$ millions cells ($1000 \times 500 \times 50$).

>>>>

CFD algorithms often require to solve linear systems with iterative methods.
For example, the projection method implemented in our software solve a Poisson system every time step to project the velocity field onto the divergence-free space (to satisfy the incompressibility constraint).
Thus, we investigated the time-to-solution to solve a three-dimensional Poisson system (obtained with a 7-point stencil central-difference scheme) on different nodes of Microsoft Azure and Colonial One.
The system was solved using a Conjugate-Gradient (CG) method with a classical Algebraic Multi-Grid (AMG) preconditioner with an exit criterion set to an absolute tolerance of $10^{-12}$.
The iterative solver ran on CPU nodes (\texttt{H16r} instances on Azure and \texttt{Short} nodes on Colonial One) using the CG algorithm from the PETSc library\cite{balay_et_al_2018} and an AMG preconditioner from Hypre BoomerAMG.
Fig. \ref{fig:poisson_benchmarks} (top) reports the mean runtimes (averaged over $5$ repetitions) to iteratively solve the system, on a uniform grid of $50$ million cells ($1000 \times 1000 \times 50$), as we increase the number of nodes in the pool.
We also solved the Poisson system with the NVIDIA AmgX library on multiple GPU devices using \texttt{NC24r} instances on Azure and \texttt{Ivygpu} nodes on Colonial One.
The Poisson system for a base mesh of $6.25$ million cells ($500 \times 500 \times 25$) is solved on a single node using $12$ MPI processes and $2$ GPU devices; we then double the mesh size as we double the number of nodes (keeping the same number of MPI processes and GPUs per node).
As the number of iterations to reach convergence increases with the size of the system, we normalize the runtimes by the number of iterations.
Fig. \ref{fig:poisson_benchmarks} (bottom left) shows the normalized mean runtimes ($5$ repetitions) obtained on Azure and Colonial One.
The smaller runtimes on Azure are explained by the fact the NC-series of Microsoft Azure features NVIDIA K80 GPU devices with a higher compute capability than the K20 GPUs on Colonial One.
The bottom-right panel of the figure reports the normalized mean runtimes obtained on Azure when we put more constraint on the bandwidth; the base mesh now contains $25$ millions cells ($1000 \times 500 \times 50$).
We observe larger variations in the time-to-solution for the Poisson system on Microsoft Azure; runtimes are more constant on Colonial One.
